\herschel\footnote{{\it Herschel} is an ESA space observatory with science instruments provided by European-led Principal Investigator consortia and with important participation from NASA.} Orion Protostar Survey (HOPS) Imaging and Photometry Results.

### 2017-04-30 HOPS/photometry/ms.tex
updated references and minor tweaks on text

Unfortunately, this strong link to their surroundings also makes protostars difficult to study.  In particular:  (i) observational studies must be able to disentangle the degenerate effects of both the environment and the star-formation process itself.  Protostars are characterized by a central core, an accretion disk, outflows, and an infalling envelope \citep{ali}. Additionally, protostars alter their local environment with phenomenon such as Herbig-Haro objects \citep{hhobjects}.  The spatial scales for all of these components range from less than 1 AU to 100s of AUs \citep{mo07}.  Thus, observational strategies must account for this compact, yet complicated morphology.  Further, (ii) the presence of dust in the local environment means the amount of extinction in lines-of-sight to star formation regions is abnormally high (few to several tens of magnitudes in the visual) compared to most of the rest of the Galaxy \citep{dobbs}.  Finally, (iii)  \spitzer\ and \herschel\ observations, in particular, confirmed long recognized views that far-IR observations of the reprocessed radiation can probe the evolution of protostars \citep{als87}.  The presence of an infalling envelope of gas and dust is a defining characteristic of protostars. This envelope absorbs the radiation from the central accreting star+disk and reprocesses most of the luminosity into the far-IR \citep{ali}.   Far-IR observations are, therefore, absolutely crucial for efficiently identifying and studying protostars because protostars emit most of their light at those wavelengths.

@@

The  \herschel\ Orion Protostar Survey (HOPS) Open Time Key Program (PI: S. T. Megeath) was motivated by the availability of sensitive far-infrared measurements to address the challenges, (i) -- (iii), mentioned above.  HOPS uses a combination of strategies to mitigate these issues.  First, we use multi-wavelength measurements to disentangle the protostar's components.  Multi-wavelength measurements are useful because they directly connect the emergent spectral properties with the underlying physical structure and conditions of said protostar component.  As these conditions vary between the components, they also vary in the emergent emission.  

@@

Second, we focus on the nearby star-forming region, Orion \citep{orion}.  Orion provides several key advantages.  \cite{orion} identified a rich sample of protostars in Orion from \spitzer\ thus providing us a collection of protostars in a variety of environmental conditions.  Star formation has been observed in a rich diversity of environments, from isolated cold globules to rich clusters. See, for example, \cite{carpenter}, \cite{feigelson}, \cite{amy2010}.   Also, at 419 pc \citep{schlafly} , Orion is relatively nearby and, thus, allows relatively high spatial resolution to resolve morphologies.

@@

Finally, the inclusion of \herschel\ data, in particular, allowed us to directly measure the emission from the protostellar envelopes, and mitigate the effects of extinction.   The extinction at infrared and radio wavelengths is orders of magnitude lower than at optical wavelengths \citep{extinction}.  The unprecedented sensitivity afforded by \herschel\ at far-infrared wavelengths allowed us to efficiently sample a large number of protostars.

@@

\section{Protostar sample \& observations}
\label{sec:sample}
\par
The \spitzer\ Orion protostar sample was defined and described by \cite{orion}.  We selected a flux-limited subset of 280 protostars for follow-up with \herschel\  for HOPS.  The number of targets for the HOPS follow-up was limited solely by signal-to-noise ratio (S/N) considerations.  Our original sample of 280 \herschel\ targets were segregated in distinct spatial tiles to optimize observing.  The tiles were assigned consecutive three-digit integer group numbers starting with the number 0 (zero).  The spatial sizes of the tiles ranged from 3\arcmin\ (most common) to 7\arcmin).  The protostar candidates selected for our \herschel\ survey are referred to as the HOPS sources and are uniquely identified by a 3-digit integer number starting with the number 0 (zero).   Ultimately, we detected additional candidates previously identified in the \spitzer\ survey whose spatial location happened to be within the field-of-view of the observation tile.  These sources, however, were not part of the original HOPS candidate list because their estimated fluxes were below our S/N limit.  Further, \cite{pbrpaper} found protostars and candidates not identified in the \spitzer\ list; See section~\ref{sec:protostars} for more details.  Our final catalog appends the original sample of 280 targets with the additions mentioned above.  There are a total of 410 sources in the final sample included here.
\par
\cite{furlan}\ classified 330 of these sources as young stellar objects (YSOs) and the remaining as unlikely to be protostars and/or sources not observed or detected by PACS at 70~micron.  For their analysis, and sdcs\cite{furlan} focus on the 330 HOPS targets which have complete \spitzer\ and \herschel\ data (at least a PACS 70~\micron\ detection) and most were originally considered protostars by \cite{orion}.  The objective of this contribution is to provide complete data on all sources from our original sample of 280 protostars as well as the additional targets detected in our images.  Thus, we have included all 410 objects in this contribution.

\subsection{Observing strategy}
\label{sec:obs}
\par
For the HOPS Key Program, we used the PACS instrument \citep{pacs}, and the scan-map Astronomical Observing Template (AOT) with the 20\arcsec/second scan speed.  The scan map AOT offers several advantages over the point source, small source, and raster AOTs: (i) scan-map AOTs ultimately provide the best sky sampling.  (ii) Scanning allows efficient mapping of groups of point-sources within individual spatial tiles.  And, (iii) PACS' non-scan AOTs must employ chopping to remove background and low- frequency drifts; Chopping cannot provide optimal removal of these effects in spatially confused regions such as the protostellar fields in Orion.

\par
We used the slowest allowed scan speed (20\arcsec/second ) to avoid beam smearing and to preserve the best possible spatial resolution.   By design, the PACS instrument observed both the 70~\micron\ and 160~\micron\ filters simultaneously.  Each group of stars (spatial tile) was observed in two scan directions to avoid the so-called {\em striping}\ defect common to bolometer arrays \citep{boloref}.  These two scan directions form two distinct \herschel\ Astronomical Observing Requests (AORs).  Hence, each group in our observations is assigned two separate unique identifiers, called OBSIDs.  The two AORs per group are concatenated and were, therefore, assigned sequential OBSIDs.  Typically, several scans are needed to cover our spatial tiles given that the size of the spatial tiles (see above) is larger than the PACS field-of-view.  We allowed the PACS observing template to automatically calculate the number of scans and overlap between each scan for our required sensitivity and tile size.  Our observing template observed the spatial tile with uniform coverage.

\subsection{The observed protostar sample}
\label{sec:protostars}
Table~\ref{tbl:obs} lists the final combined catalog (see below for Table details).  As noted above, in some groups, we coincidently observed additional protostars from the \citet{orion} \spitzer\ sample.  These sources happen to be located inside group fields-of-view.   Of note, \citet{pbrpaper} identified highly embedded additional protostars (the so-called PACS Bright Red Sources, PBRs).  Our final catalog includes all known protostars detected by \herschel\ in the Orion fields covered by our observations.
\par
We investigated HOPS images for additional protostar candidates that might have been missed by our earlier efforts.  \citet{pbrpaper} required a 160~\micron\ detection for improved reliability, and implemented additional thresholds to reduce contamination from extra-galactic sources.  As \citet{pbrpaper} showed, \spitzer\ observations did not identify, or in rare cases, detect all protostars in Orion.  Hence, the possibility remains that additional sources, perhaps with detections only in the 70~\micron\ filter, lurk within our data.  With detection in only one or two bands, however, it is increasingly difficult to properly characterize these sources and distinguish them from foreground or background objects.  It is likely necessary that additional protostar candidates here will require follow-up observations or analysis.  Nonetheless, these sources may impact statistical studies, and are tabulated.  The results of this effort will be described in a future contribution.
\par
The columns have the following meaning in Table~\ref{tbl:obs}.  Column~1 lists the unique three-digit HOPS identifier.  Columns~2~\&~3 list the J2000 equatorial coordinates as measured on the \herschel\ images and as reported by the DAOPHOT find algorithm \citep{psfphotometry}.  Column~4 lists the \herschel-assigned unique observation identifiers (OBSIDs, two per group as described in Section~\ref{sec:obs}).  Column~5 lists the 3-digit group number mentioned above.  Columns~6-13 list the \herschel\ photometry for the three Herschel/PACS bands.  Note these results were already reported by \cite{furlan} and are repeated here for convenience.  Our photometry procedure is described in Section~\ref{sec:phot}.  The 70~\micron\ and 160~\micron\ flux densities are from our program.  The 100~\micron\ fluxes are added from the larger survey of the Orion region from the the Gould-Belt Key Program \citep{gb}.  The extraction of the 100\micron\ photometry is discussed in \cite{pbrpaper}.  Each photometry value is described by three columns: the first provides the photometry value itself, the second, labelled flag, has the following meaning:   flag = 0 means the source is not observed. flag =1 means the photometry, as quoted, is the measured value,  flag = 2 means the value is an upper limit, and flag = 3 means that the measurement is from the PSF-photometry, not aperture photometry (see Section~\ref{sec:phot}).  The third column labelled 'Method' lists whether aperture or PSF photometry technique was used to obtain the measurement.  Column~14 identifies the sub-region within the Orion~A and B clouds to which the HOPS source belongs.  The sub-region definitions are listed in Table~\ref{tbl:regions}.  Finally, Column~15 lists the UT observation day for the observations.  When a source was detected in more than one group (tile) we combined the measurements as a simple average.

\section{Data Processing \& Map-making}
\label{sec:dp}
\par
We start data processing at the level~1 stage from the Herschel Science Archive.  Level~1 contains calibrated timelines\footnote{Timelines are simply readouts from individual pixels ordered sequentially by time of observation.  Note that for our observations the PACS instrument was used with a fixed readout frequency of 10 Hz.} from individual PACS bolometers from which all instrumental effects have already been removed except for the low frequency noise component (the so-called 1/f noise\footnote{The so-called 1/f noise modifies the signal timelines by adding a drift component whose amplitude is a power-law function of its Fourier frequency.}).  Our processing mitigates the 1/f noise, combines the two independent orthogonal scan directions, and projects the timelines onto the final image of the field.  We will refer to these steps as 'map-making' hereafter.  The processing steps leading up to level~1 are described in \citet{pacs} and in the data processing guides for the Herschel Interactive Processing System, HIPE \cite{hipe}.  All data discussed here are based on the FM7 version of the PACS calibration \citep{pacscal} and processed with version 9 of the HIPE software.  Our final maps have spatial scales of 1.6\arcsec/pixel and 3.2\arcsec/pixel for the 70~\micron\ and 160~\micron\ PACS filters, respectively.  We used two different approaches for map-making that are described below.

@@

>>>>

Unfortunately, this strong link to their surroundings also makes protostars difficult to study.  In particular:  (i) observational studies must be able to disentangle the degenerate effects of both the environment and the star-formation process itself.  Protostars are characterized by a central core, an accretion disk, outflows, and an infalling envelope \citep{ali}. Additionally, protostars alter their local environment with phenomenon such as Herbig-Haro objects \citep{hhobjects}.  The spatial scales of these components range from sub-AU to 100s of AUs \citep{mo07}.  Thus, observational strategies must account for this compact, yet complicated morphology.  (ii) The presence of dust in the local environment means the amount of extinction in lines-of-sight to star formation regions is abnormally high (few to several tens of magnitudes in the visual) compared to most of the rest of the Galaxy \citep{dobbs}.  Finally, (iii)  \spitzer\ and \herschel\ observations, in particular, confirmed long recognized views that far-IR observations of the reprocessed radiation can probe the evolution of protostars \citep{als87}.  The presence of an infalling envelope of gas and dust is a defining characteristic of protostars. This envelope absorbs the radiation from the central accreting star+disk and reprocesses most of the luminosity into the far-IR \citep{ali}.   Far-IR observations are, therefore, absolutely crucial for efficiently identifying and studying protostars because protostars emit most of their light at those wavelengths.

@@

The  \herschel\ Orion Protostar Survey (HOPS) Open Time Key Program (PI: S. T. Megeath) was motivated by the availability of sensitive far-infrared measurements to address the challenges, (i) -- (iii), mentioned above.  HOPS uses a combination of strategies to mitigate these issues.  First, we use multi-wavelength measurements to disentangle the protostar's components.  Multi-wavelength measurements are useful because they directly connect the emergent spectral properties with the underlying physical structure and conditions of said protostar component.  As these conditions vary between the components, they also vary in the emergent emission.  Thus, the overall SED of the source may be modeled as the sum of contributions from the individual components (see, \eg, Furlan \etal\ 2016, Ali \etal\ 2010).

@@

Second, we focus on the nearby star-forming region, Orion \citep{orion}.  Orion provides several key advantages.  Star formation has been observed in a rich diversity of environments, from isolated cold globules to rich clusters. See, for example, \cite{carpenter}, \cite{feigelson}, \cite{amy2010}.   \cite{orion} identified a rich sample of protostars from \spitzer\ thus providing us a collection of protostars in a variety of environmental conditions.  And, at 419 pc \citep{schlafly} , Orion is relatively nearby and, thus, affording relatively high spatial resolution to resolve morphologies.

@@

Finally, the use of \herschel\ data, in particular, allowed us to directly measure the emission from the protostellar envelopes, and mitigate the effects of extinction.   The extinction at infrared and radio wavelengths is orders of magnitude lower than at optical wavelengths \citep{extinction}.  The unprecedented sensitivity afforded by \herschel\ at far-infrared wavelengths allowed us to efficiently sample a large number of protostars.

@@

\section{Protostar sample \& observations}
\label{sec:sample}
\par
The \spitzer\ Orion protostar sample was defined and described by \cite{orion}.  We selected a flux-limited subset of 280 protostars for follow-up with \herschel\  for HOPS.  The number of targets for the HOPS follow-up was limited solely by signal-to-noise ratio (S/N) considerations.  Our original sample of 280 \herschel\ targets were segregated in distinct spatial tiles to optimize observing.  The tiles were assigned consecutive three-digit integer group numbers starting with the number 0 (zero).  The spatial sizes of the tiles ranged from 3\arcmin\ (most common) to 7\arcmin).  The protostar candidates selected for our \herschel\ survey are referred to as the HOPS sources and are uniquely identified by a 3-digit integer number starting with the number 0 (zero).   Ultimately, we detected additional candidates previously identified in the \spitzer\ survey whose spatial location happened to be within the field-of-view of the observation tile.  These sources, however, were not part of the original HOPS candidate list because their estimated fluxes were below our S/N limit.  Further, \cite{pbrpaper} found protostars and candidates not identified in the \spitzer\ list; See section~\ref{sec:protostars} for more details.  Our final catalog appends the original sample of 280 targets with the additions mentioned above.  There are a total of 410 sources in the final sample included here.
\par
\cite{furlan}\ classified 330 of these sources as young stellar objects (YSOs) and the remaining as unlikely to be protostars and/or sources not observed or detected by PACS at 70~micron.  For their analysis, \cite{furlan} focused on the 330 HOPS targets which have complete \spitzer\ and \herschel\ data (at least a PACS 70~\micron\ detection) and most were originally considered protostars by \cite{orion}.  The objective of this contribution is to provide complete data on all sources from our original sample of 280 protostars as well as the additional targets detected in our images.  Thus, we have included all 410 objects in this contribution.

\subsection{Observing strategy}
\label{sec:obs}
\par
We used the PACS instrument \citep{pacs}, and the scan-map Astronomical Observing Template (AOT) with the 20\arcsec/second scan speed for all HOPS observations.  The scan map AOT offers several advantages over the point source, small source, and raster AOTs: (i) scan-map AOTs ultimately provide the best sky sampling.  (ii) Scanning allows efficient mapping of groups of point-sources within individual spatial tiles.  And, (iii) PACS' non-scan AOTs must employ chopping to remove background and low- frequency drifts; Chopping cannot provide optimal removal of these effects in spatially confused regions such as the protostellar fields in Orion.

\par
We used the slowest allowed scan speed (20\arcsec/second ) to avoid beam smearing and to preserve the best possible spatial resolution.   By design, the PACS instrument observed both the 70~\micron\ and 160~\micron\ filters simultaneously.  Each group of stars (spatial tile) was observed in two scan directions to avoid the so-called {\em striping}\ defect common to bolometer arrays \citep{boloref}.  These two scan directions form two distinct \herschel\ Astronomical Observing Requests (AORs).  Hence, each group in our observations is assigned two separate unique identifiers, called OBSIDs.  The two AORs per group are concatenated and were, therefore, assigned sequential OBSIDs.  Typically, several scans are needed to cover our spatial tiles given that the size of the spatial tiles (see above) is larger than the PACS field-of-view.  We allowed the PACS observing template to automatically calculate the number of scans and overlap between each scan for our required sensitivity and tile size.  Our observing template observed the spatial tile with near uniform coverage.

\subsection{The observed protostar sample}
\label{sec:protostars}
Table~\ref{tbl:obs} lists the final combined catalog (see below for detailed description of columns).  As noted above, in some groups, we coincidently observed additional protostars from the \citet{orion} \spitzer\ sample.  Of note, \citet{pbrpaper} identified highly embedded additional protostars (the so-called PACS Bright Red Sources, PBRs).  Our final catalog includes all known protostars detected by \herschel\ in the Orion fields covered by our observations.
\par
We also investigated HOPS images for additional protostar candidates that might have been missed by our earlier efforts.  \citet{pbrpaper} required a 160~\micron\ detection for improved reliability, and implemented additional thresholds to reduce contamination from extra-galactic sources.  As \citet{pbrpaper} showed, \spitzer\ observations did not identify, or in rare cases, detect all protostars in Orion.  Hence, the possibility remains that additional sources, perhaps with detections only in the 70~\micron\ filter, lurk within our data.  With detection in only one or two bands, however, it is increasingly difficult to properly characterize these sources and distinguish them from foreground or background objects.  It is likely necessary that additional protostar candidates here will require follow-up observations or analysis.  Nonetheless, these sources may impact statistical studies, and are tabulated.
\par
The columns have the following meaning in Table~\ref{tbl:obs}.  Column~1 lists the unique three-digit HOPS identifier.  Columns~2~\&~3 list the J2000 equatorial coordinates as measured on the \herschel\ images and as reported by the DAOPHOT find algorithm \citep{psfphotometry}.  Column~4 lists the \herschel-assigned unique observation identifiers (OBSIDs, two per group as described in Section~\ref{sec:obs}).  Column~5 lists the 3-digit group number mentioned above.  Columns~6-13 list the \herschel\ photometry for the three Herschel/PACS bands.  Note these results were already reported by \cite{furlan} and are repeated here for convenience.  Our photometry procedure is described in Section~\ref{sec:phot}.  The 70~\micron\ and 160~\micron\ flux densities are from our program.  The 100~\micron\ fluxes are added from the larger survey of the Orion region from the the Gould-Belt Key Program \citep{gb}.  The extraction of the 100\micron\ photometry is discussed in \cite{pbrpaper}.  Each photometry value is described by three columns: the first provides the photometry value itself, the second, labelled flag, has the following meaning:   flag = 0 means the source is not observed. flag =1 means the photometry, as quoted, is the measured value,  and flag = 2 means the value is an upper limit.  The third column, 'Method' identifies whether the measurement is from aperture photometry (A) or PSF-photometry (P).  Column~14 identifies the sub-region within the Orion~A and B clouds to which the HOPS source belongs.  The sub-region definitions are listed in Table~\ref{tbl:regions}.  Finally, Column~15 lists the Universal Time (UT) observation day for the observations.  Note: when a source was detected in more than one group (tile) we combined the measurements as a simple average.

\section{Data Processing \& Map-making}
\label{sec:dp}
\par
We start data processing at the so-called level~1 stage from the Herschel Science Archive \citep{pacspipeline}.  Level~1 contains calibrated timelines\footnote{Timelines are simply readouts from individual pixels ordered sequentially by time of observation.  Note that for our observations the PACS instrument was used with a fixed readout frequency of 10 Hz.} from individual PACS bolometers from which all instrumental effects have already been removed except for the low frequency noise component (the so-called 1/f noise\footnote{The so-called 1/f noise modifies the signal timelines by adding a drift component whose amplitude is a power-law function of its Fourier frequency.}).  Our processing mitigates the 1/f noise, combines the two independent orthogonal scan directions, and projects the timelines onto the final image of the field.  We will refer to these steps as 'map-making' hereafter.  The processing steps leading up to level~1 are described in \citet{pacs} and in the data processing guides for the Herschel Interactive Processing System, HIPE \cite{hipe}.  All data discussed here are based on the FM7 version of the PACS calibration \citep{pacscal} and processed with version 9 of the HIPE software.  Our final maps have spatial scales of 1.6\arcsec/pixel and 3.2\arcsec/pixel for the 70~\micron\ and 160~\micron\ PACS filters, respectively.  We used two different approaches for map-making that are described below.

@@

\bibitem[Wieprecht \etal\ (2009)]{pacspipeline}Wieprecht, E., Schreiber, J., de Jong, J., \etal, 2009, ASP Conf. Ser., 411, 531
